### 2024-04-14 introduction.tex
small changes to intro

Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. 
For complex financial products, such as option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the multifaceted nature of market, credit, and operational risks. 
This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model complex financial and actuarial products.

>>>>

Quantitative risk management is a key component of modern financial systems, ensuring the stability and resilience of markets, institutions, and portfolios against an array of risks. 
For financial products like option portfolios and variable annuity contracts, traditional risk assessment methods often fall short in accurately capturing the complex dynamics of the underlying risk factors.
This is where advanced Monte Carlo simulation techniques, particularly nested simulation procedures, become indispensable.
In contrast to finite-difference methods, a Monte Carlo simulation scheme is more flexible and can be easily adapted to model complex dynamics with a rule-based design.
